---
title: "covid19Visualizer"
author: "Adrian Joseph"
date: "3/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('covid19Visualizer')
library('kableExtra')
```

#Introduction

Simple data visualizer for COVID-19 diffusion.

## Data

Data is provided by Johns Hopkins University and is obtained from <https://github.com/CSSEGISandData/COVID-19>.

New data is obtained with (a network connection is required):

```{r getNewData}
newData <- refreshData()
```

## Plot a single metric

The data provide time series for total cases, deatsh and recoveries.

Each metric can be plotted for selected countries using:

```{r doPlot}
# cases
doPlot(newData, 'cases', c('Italy', 'China'))

# deaths
doPlot(newData, 'deaths', c('Italy', 'China'))

# recovered
doPlot(newData, 'recovered', c('Italy', 'China'))
```

Each plot can be plotted in log10 scale:
```{r doPlotLog}
# cases
doPlot(newData, 'cases', c('Italy', 'China'), scale = 'log')

# deaths
doPlot(newData, 'deaths', c('Italy', 'China'), scale = 'log')

# recovered
doPlot(newData, 'recovered', c('Italy', 'China'), scale = 'log')
```

We can also plot the variation, rather than the raw numbers:
```{r doPlotRate}
# cases
doPlot(newData, 'cases', c('Italy', 'China'), plotDiff = TRUE)

# deaths
doPlot(newData, 'deaths', c('Italy', 'China'), plotDiff = TRUE)

# recovered
doPlot(newData, 'recovered', c('Italy', 'China'), plotDiff = TRUE)
```

## Plot all metrics for selected countires

```{r plotAllMetrics}
# linear
plotAllMetrics(newData, c('Italy', 'China'))

# log
plotAllMetrics(newData, c('Italy', 'China'), scale = 'log')
```

And the rate:

```{r plotAllMetricsRate}
plotAllMetrics(newData, c('Italy', 'China'), plotDiff = TRUE)
```

## Map plots

### General overview
```{r mapPlots}
# Simple plot
doMap(rawData = newData, normalizeByPopulation = FALSE, filterByCountry = NULL,
      removeCountries = NULL, chosenDay = NULL, showTrend = FALSE)

# A specific day
doMap(rawData = newData, normalizeByPopulation = FALSE, filterByCountry = NULL,
      removeCountries = NULL, chosenDay = 210, showTrend = FALSE)

# Specific countries
doMap(rawData = newData, normalizeByPopulation = FALSE,
      filterByCountry = c('Italy', 'Spain'),
      removeCountries = NULL, chosenDay = 210, showTrend = FALSE)

# Normalise by population
doMap(rawData = newData, normalizeByPopulation = TRUE,
      filterByCountry = c('Italy', 'Spain'),
      removeCountries = NULL, chosenDay = 210, showTrend = FALSE)

# Show mean trend of past 10 days
# This will always set normalizeByPopulation = FALSE and chosenDay = NULL
doMap(rawData = newData, normalizeByPopulation = FALSE,
      filterByCountry = c('Italy', 'Spain'),
      removeCountries = NULL, chosenDay = NULL, showTrend = TRUE)
```

### Quarantine countries

UK impose qurantine for traveller coming from certain countries. One of the criteria used is that a countru should not have more than a total of 20 new cases every 100,000 inhabitants over the past 7 days. The following plots will show countries above or below such threshold.

```{r mapQPlots}
# plot heatmap of total number of cases every 100k subjects for the past 7 days
doQMap(refreshData(FALSE, FALSE), c('Italy', 'Spain'), categoricalPlot = FALSE)
# plot categorical of total number of cases every 100k subjects for the past 7
# red >= 20 , blue < 20
doQMap(refreshData(FALSE, FALSE), c('Italy', 'Spain'), categoricalPlot = TRUE)
```

## Summary table

```{r summaryTable}
kable(getSummaryTable(newData))
```

